Language-Based Security for Low-Level MPC

### 2024-05-17 ppdp24/hyper.tex
checkpoint

\section{Security Hyperproperties}

@@

\emph{Integrity} is an important hyperproperty in security models that admit
malicious adversaries. Consistent with formulations in deterministic settings,
we have already defined protocol confidentiality as the preservation of low equivalence
(of secrets and views), and now we define protocol integrity as the preservation
of high equivalence (of secrets and views). Intuitively, this property says
that any adversarial strategy either ``mimics'' a passive strategy with some
choice of inputs or causes an abort.
\begin{definition}[Integrity]
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
A first important observation is that integrity preserves protocol correctness
for honest outputs, except for the possibility of abort. 
\begin{lemma}
  \label{lemma-malicious-correct}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is passive correct for
  $\idealf$ and
  has integrity, then for all $H$, $C$, and $\adversary$ and $\store_1 \in \mems(S_H)$,
  there exists $\store_2 \in \mems(S_C)$ such that:
  $$
  \idealf(\store_1 \cap \store_2)_H \cup \{ \bot \} \supseteq
    \support(\progtt(\prog,\adversary)(O_H|\store_1))
  $$
\end{lemma}
The following result establishes that integrity implies malicious
security for protocols that are passive secure (which also subsumes
correctness). 
\begin{theorem}
  If a protocol is passive secure and has integrity, then it
  is malicious secure.
\end{theorem}

>>>>

\section{Security Hyperproperties}
\label{section-hyper}

@@

\emph{Integrity} is an important hyperproperty in security models that admit
malicious adversaries. Consistent with formulations in deterministic settings,
we have already defined protocol confidentiality as the preservation of low equivalence
(of secrets and views), and now we define protocol integrity as the preservation
of high equivalence (of secrets and views). Intuitively, this property says
that any adversarial strategy either ``mimics'' a passive strategy with some
choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ 
  then there exists $\store' \in \mems(S)$ with $\store_{S_H} = \store'_{S_H} $ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{\store_{S_H \cup \cinputs}} =
    \condd{\progtt(\prog)}{X}{\store'}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
A first important observation is that integrity preserves protocol correctness
for honest outputs, except for the possibility of abort. 
\begin{lemma}
  \label{lemma-malicious-correct}
  If a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ is passive correct for
  $\idealf$ and
  has integrity, then for all $H$, $C$, and $\adversary$ and $\store_1 \in \mems(S_H)$,
  there exists $\store_2 \in \mems(S_C)$ such that:
  $$
  \idealf(\store_1 \cap \store_2)_H \cup \{ \bot \} \supseteq
    \support(\progtt(\prog,\adversary)(O_H|\store_1))
  $$
\end{lemma}
The following result establishes that integrity implies malicious
security for protocols that are passive secure (which also subsumes
correctness). 
\begin{theorem}
  \label{theorem-integrity}
  If a protocol is passive secure and has integrity, then it
  is malicious secure.
\end{theorem}

### 2024-05-17 ppdp24/intro.tex
checkpoint

Nevertheless, as previous authors have observed \cite{XXX}, low-level
protocol design patterns such as secret sharing and circuit gate
structure have compositional properties that can be abstracted and
leveraged in larger proof contexts. We contribute to this line of work
by developing an automated verification technique for subprotocols and
show how it can be integrated as a tactic in a larger security proof.

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
characteristics of protocols and precisely quantifying allowable
information leakage in terms of protocol outputs. On this basis we can
formulate security hyperproperties, including \emph{noninterference
modulo output ($\NIMO$)} that implies passive simulator security. But
program distributions are flexible and can be used to certify other
important properties of protocol components, such as probabilistic
independence, correlation, and distributions under conditioning.

\paragraph{Fully and partially automated verification.} In Section
\ref{section-automation} we develop an automated technique, aka
certification, for automatically verifying security properties such as
$\NIMO$ and other supporting properties of protocol components.  While
certification has high complexity, a compositional approach allows
certification of program components in isolation.  This enables a
semi-automated method for large circuits where we (1) define
certification for components, (2) certify components, (3) prove
$\NIMO$ based on the certifiedness of components. We develop novel
methods partially based on separation logic
\cite{barthe2019probabilistic} to enable (3).  In Section
\ref{section-composition} we illustrate our method to obtain
semi-automated verification for the GMW and Yao's Garbled
Circuit protocols, where certification can be re-used to validate new
gate implementations.

>>>>

Nevertheless, as previous authors have observed \cite{XXX}, low-level
protocol design patterns such as secret sharing and circuit gate
structure have compositional properties that can be independently
verified and then leveraged in larger proof contexts. We
contribute to this line of work by developing an automated
verification technique for subprotocols and show how it can be
integrated as a tactic in a larger security proof.

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-model} we
develop our formalism for expressing the joint probability mass function of
program variables, and give standard definitions of passive and
malicious real/ideal security in our model. In Section
\ref{section-hyper}, we formulate a variety of familiar information
flow properties in our probabilistic setting, including condition
noninterference, delimited release, and robust declassification, and
consider the relation between these and real/ideal security.  While it
has been previously shown that probabilistic conditional
noninterference is sound for passive security, we formulate new
properties of integrity which, paired with passive security, imply
malicious security (Theorem \ref{theorem-integrity}). We observe
in Section \ref{section-example-bdoz} that authentication mechanisms
such as BDOZ/SPDZ style MACs enforce a strictly weaker property
of ``cheating detection''.

\paragraph{Fully and partially automated verification.} In Section
\ref{section-bruteforce} we develop a method for automatically
computing the pmf of $\minifed$ protocols in $\mathbb{F}_2$, that can
be automatically queried to enforce hyperperproperties of
security. This method is perfectly accurate but has high complexity;
we show this can be partially mitigated by conversion of protocols in
$\mathbb{F}_2$ to stratified Datalog which is amenable to HPC
acceleration. Furthermore, in Section \ref{section-examples-gmw} we
consider in detail how this automated technique can be used as a local
automated tactic for proving security in arbitrarily large GMW
circuits using conditional probabilistic independence as in
\cite{XXX}.
